The impact of cosmic variance on simulating weak lensing surveys

### 2015-02-26 Writeup/reply.tex
more editing of reply - done now

Please find below a point-by-point response to the referee report.

@@

We performed the analysis again using a random subset of 50 per cent of the galaxies in overdense
regions, keeping the underdense bins intact. The uncertainities in the overdense bins increase due
to smaller sample size. However, the difference is not significant enough to alter our conclusions
based on the $p$-values from the KS and AD tests. We have noted this in Section 4.2.

@@

Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As we have verified and pointed out in the paper after revision,
the neutral bins in our sample consists of overdensities and underdensities making it look like neutral in the number count. However, there are more galaxies in the OD regions than in the UD regions thus making the quantities measured more overdense-like. In almost all of the scatterplots (Figs.9-11), the green points (neutral)tend to line up with the red points (OD). 
\end{document}

>>>>

@@

We performed the analysis again using a random subset of 50 per cent of the galaxies in overdense
regions, keeping the underdense bins intact. The uncertainties in the overdense bins increase due
to smaller sample size. However, the difference is not significant enough to alter our conclusions
based on the $p$-values from the KS and AD tests. We have noted this in Section 4.2.

@@

Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As
we have verified and pointed out in Section 4.2 of the revised papern,
the neutral bins in our sample consist of mixtures of clear overdensities and underdensities, making
it look like roughly neutral in the number count. However, given the complex mixture of morphologies
plus the fact that more of the galaxies are in the overdense regions, the quantities measured are
more similar to those in overdense regions.  We have explained this in the new version, showed other
papers that verify the mixed nature of these regions, and believe this explanation should be enough
that the behavior of the neutral regions does not weaken our overall conclusions.

\rachel{Arun, if you have made other edits (fixes to bugs in figures etc.) then you should mention
  them here.  You can simply say ``In addition to the above changes, we made several small
  modifications that are not in response to the referee's comments.'' and then say what those
  changes are.  The referee deserves a chance to comment on them and it's easier for them if you
  point them out.}
\end{document}
